Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2024-08-20 doc/manuscript/ForC-EFDB manuscript.Rmd
fixed typo

To submit complete, reviewed ForC records tp EFDB, we created R scripts to restructure ForC records and populate EFDB's bulk import form (publicly available; see **Data Availability Statement**).
Criteria for data submission were that
(1) records had been checked against the original study and determined to be complete and correct, and as originally presented,
(2) all relevant records within the publication were included in ForC,
(3) the original study presented values in tables or text, as opposed to the values having been digitized from graphs or calculated based on related variables,
and (4) the records had not previously been submitted to EFDB.
Review of potentially relevant records was prioritized as described in `r appendix_ForC_updates`.
Once converted into EFDB format, the records were reviewed and then sent to the IPCC's Technical Support Unit for their review and submission to EFDB.
Submissions were sent in six batches between April 2021 and June 2022, and feedback on each batch from the EFDB team was used to improve our system for subsequent submissions.

>>>>

To submit complete, reviewed ForC records to EFDB, we created R scripts to restructure ForC records and populate EFDB's bulk import form (publicly available; see **Data Availability Statement**).
Criteria for data submission were that
(1) records had been checked against the original study and determined to be complete and correct, and as originally presented,
(2) all relevant records within the publication were included in ForC,
(3) the original study presented values in tables or text, as opposed to the values having been digitized from graphs or calculated based on related variables,
and (4) the records had not previously been submitted to EFDB.
Review of potentially relevant records was prioritized as described in `r appendix_ForC_updates`.
Once converted into EFDB format, the records were reviewed and then sent to the IPCC's Technical Support Unit for their review and submission to EFDB.
Submissions were sent in six batches between April 2021 and June 2022, and feedback on each batch from the EFDB team was used to improve our system for subsequent submissions.
